Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-16 paper/uist_2016/paper.tex
updated abstract, edited reference typo

\begin{abstract}
GPS tracking using smartphones have been prevalent, providing self-trackers insights into their past visits and traveling patterns. Using tracked GPS information, we proposed \textit{Rewind}, a system that recreates sceneries of past trips to assist the recall of episodic memory. \textit{Rewind} takes historical GPS data from the users, maps out movement trajectories, and generates stitched-together videos to simulate the ways how past trips were taken. Users of \textit{Rewind} can change their moving directions by scrubbing their pointers over the video. Images used in \textit{Rewind} videos are post-processed to reveal weather and timely characteristics of the emulated environment.  Our study of self-trackers using two-week of GPS data with \textit{Rewind} has revealed that non-GPS users tend to think \textit{Rewind} videos have accurately captured their past trips, and users are particularly interested in preserving \textit{Rewind} videos of infrequent trips and trips accompanied by others. Overall, \textit{Rewind} serves as an experiment of the extreme scenario where people can freely roam and experience the world, keeping their mobile devices in their pockets, and still generate believable representations that capture the past.
\end{abstract}

@@

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. \ref{fig:flowchart}

\begin{figure}
     \includegraphics[width=1\linewidth]{Rewind-flowchart}
     \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
     \label{fig:flowchart}
\end{figure}

>>>>

\begin{abstract}
We propose \textit{Rewind}, a system that assists in the recall of episodic memory by automatically recreating interactive sceneries of past trips. \textit{Rewind} uses historical geolocation data to generate egocentric videos of earlier experiences from Google's Street View images. Since the effectiveness of memory cues is determined by their level of integration with the target memory, the images are manipulated to incorporate time-of-day, seasonal and weather information, thereby creating more faithful representation of the original experience. Users can interactively go back and forth in time by scrubbing over the video. Together, the composed \textit{Rewind} videos offer users a window into past travels. We report the results of a user study with eighteen participants conducted to collect location data over two weeks. Trips taken in groups were more likely to be recalled using \textit{Rewind} videos than trips taken alone. \textit{Rewind} also serves as an experiment of the extreme scenario where users can freely roam and experience the world, keeping their mobile devices in their pockets, and still generating believable representations that capture the past.
\end{abstract}

@@

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it. %\ref{fig:flowchart}

% \begin{figure}
%      \includegraphics[width=1\linewidth]{Rewind-flowchart}
%      \caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
%      \label{fig:flowchart}
% \end{figure}
